---
title: "Data Exploration"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup and tests, include=FALSE}

## README FIRST ##
#Read and run this chunk of code line by line in the R Console (do not press knit) - there are some questions below which you will have to answer and some logic tests to complete. Once you are happy that the conditions have been satisfied, hit 'knit' above. 

# Load your data [change the files paths to your data locations]
dat <- read.csv("Raw Data/Detection_Data_Feb_2020_Single_Project.csv", header=T)
eff <- read.csv("Raw Data/Deployment_Data_Feb_2020_Single_Project.csv", header=T)
sta <- read.csv("Raw Data/Station_Covariates_Feb_2020_Single_Project.csv", header=T)

# Timezone [Use UTC if your cameras do not correct for daylight saving time, if they do use the timezone where the data was collected]
tz <- "UTC"

# Set the "independence" interval in minutes
independent <- 30

# Set a single catagorical variable of interest from station covariates for summary graphs. If you do not have and appropriate catagory use "Project.ID".
category <- "Seismic"

# Are spatial interpolated rasters sensible for your dataset?
spatial.plots <- TRUE

# Define a colour from the R options to base the colourscheme
colour <- "lightseagreen"

##############################################################
##### DATA TESTS #############################################
##############################################################

# This code will not work unless your data passes the following checks

# 1) dat$Blank must be logical
is.logical(dat$Blank)
# If this is FALSE convert this column to TRUE/FALSE
# If you dont have a Blank column and all of you data have animals in them, run the following:
 dat$Blank <- FALSE

# 2) All dates must be in YYYY-MM-DD in 'eff' and YYYY-MM-DD HH:MM:SS in 'dat' 
# If the following return NA, change your formatting
strptime(eff$Camera.Deployment.Begin.Date[1], "%Y-%m-%d", tz="UTC")
strptime(dat$Date_Time.Captured[1], "%Y-%m-%d %H:%M:%S", tz="UTC")

# 3) the dates in 'eff$Camera.Deployment.End.Date' must be the when the camera fails, not when you check the camera. If the camera fails (due to damage or full sd card), use the last day it functions here.  

# 4) Ensure your species names are consistent - check in the list below
as.data.frame(table(dat$Species))

# 5) Ensure Number.of.Animals and doesnt have any non-numeric data in! The following should return TRUE
is.numeric(dat$Number.of.Animals)

# 6) ensure all deployment dates are before retreival dates for each deployment
# Logic = are the stations active for 0 or more days -> all should read TRUE
table((strptime(eff$Camera.Deployment.End.Date, "%Y-%m-%d", tz="UTC")-strptime(eff$Camera.Deployment.Begin.Date, "%Y-%m-%d", tz="UTC"))>=0)

# 7) Do you have lat/long data for all of your sites you have effort data for? If yes, the value should be 0
length(setdiff(eff$Deployment.Location.ID, sta$Deployment.Location.ID))
# If length > 0, then you have some data missing!

# If all of the above is satisfied -> press 'Knit' above ^

```


```{r non-adjustable options, echo=F, include=F}
#Load Packages
list.of.packages <- c("leaflet", "dplyr", "colortools", "kriging", "corrplot", "lubridate")

# Check you have them and load them
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

lapply(list.of.packages, require, character.only = TRUE)

# Prepare dates
eff$Camera.Deployment.Begin.Date <- as.POSIXct(strptime(eff$Camera.Deployment.Begin.Date, "%Y-%m-%d", tz ))
eff$Camera.Deployment.End.Date <- as.POSIXct(strptime(eff$Camera.Deployment.End.Date, "%Y-%m-%d", tz ))

eff$Days <- as.numeric(round(difftime(eff$Camera.Deployment.End.Date, eff$Camera.Deployment.Begin.Date, units="days"),1))

dat$Date_Time.Captured <- as.POSIXct(strptime(dat$Date_Time.Captured, "%Y-%m-%d %H:%M:%S", tz ))

# Count the number of camera ststions
n.stat <- length(unique(eff$Deployment.Location.ID))

# Generate colours to display the catagory levels - R needs them as a factor
sta[,category] <- factor(sta[,category])
col.cat <- wheel(colour, num = length(levels(sta[,category])))
sta$Cols <- col.cat[sta[,category]]

# How big should the figures be
eff.height <- 8
if(length(unique(eff$Deployment.Location.ID))>80)
   {
     eff.height <- length(unique(eff$Deployment.Location.ID))/10
   }

sp.height <- 7
if(length(unique(dat$Species))>20)
   {
     sp.height <- 7+(length(unique(dat$Species))/8)
   }


```

## `r dat$Project.ID[1]` Project

### Camera locations

To date there have been camera deployments at `r n.stat` unique locations.

```{r map, echo=F}

m <- leaflet() %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Satellite") %>%  # Add satellite data
  addProviderTiles(providers$Esri.WorldTopoMap, group="Base") %>%     
  addCircleMarkers(lng=sta$Longitude, lat=sta$Latitude,
                   color=sta$Cols,
                   popup=paste(sta$Deployment.Location.ID, sta[,category])) %>%
 addLegend("bottomleft", colors = col.cat,  labels = levels(sta[,category]),
    title = category,
    labFormat = labelFormat(prefix = "$"),
    opacity = 1
  ) %>%
  # Layers control
  addLayersControl(
    baseGroups = c("Satellite", "Base"),
    options = layersControlOptions(collapsed = FALSE)
  )
m


```

### Camera activity through time

The `r n.stat` stations have resulted in a total of `r as.character(round(sum(eff$Days, na.rm=T),0))` camera days (mean = `r round(mean(aggregate(Days~Deployment.Location.ID, data=eff,  FUN=sum, na.rm=T)$Days),1)` days per station; min = `r round(min(aggregate(Days~Deployment.Location.ID, data=eff,  FUN=sum, na.rm=T)$Days),1)`; max = `r round(max(aggregate(Days~Deployment.Location.ID, data=eff,  FUN=sum, na.rm=T)$Days),1)`).The daily break down of camera activity is as follows:

```{r activity, echo=F, fig.height=eff.height}

# Adjust layout
par(mar=c(2,6,1,1))
plot(c(min(eff$Camera.Deployment.Begin.Date, na.rm=T), max(eff$Camera.Deployment.End.Date, na.rm=T)),      c(1,n.stat), las=1, ylab="", xlab="", type="n", yaxt="n")

# Have the first station plot at the top 
plot.order <- rev(unique(eff$Deployment.Location.ID))

axis(2, at= 1:n.stat, labels= plot.order, las=1, cex.axis=0.4)
#mtext("Camera Deployment ID", 2, 4)
# Make lines for each of the cameras
for(i in 1:length(plot.order))
{
  abline(h=i, col=rgb(0,0,0,0.1))
  tmp <- eff[eff$Deployment.Location.ID==plot.order[i],]
  for(j in 1:nrow(tmp))
    {
      lines(c(tmp$Camera.Deployment.Begin.Date[j],
                       tmp$Camera.Deployment.End.Date[j]),
            c(i,i), lwd=2)
    }
  
}

```

Figure 2: Where black lines denote a camera which is active, white space indicates cameras which are inactive. 

## Raw camera detections

To date, there have been `r nrow(dat)` image classifications, `r nrow(dat[dat$Blank==FALSE,])` of which are classified as containing identified species (`r round((nrow(dat[dat$Blank==TRUE,])/nrow(dat))*100,1)`%).

Of the detections which have been identified, there are `r length(levels(factor(dat$Species)))` different catageories. 

```{r captures, echo=F, fig.height=sp.height}
layout(matrix(c(1,1,2), 1, 3, byrow = TRUE))
det.sum.total <- as.data.frame(count(dat[dat$Blank==FALSE & is.na(dat$Species)==FALSE,], Species))
det.sum.total <- det.sum.total[order(det.sum.total$n),]

par(mar=c(5,16,1,1))
barplot(det.sum.total$n, names.arg = paste0(det.sum.total$Species, 
                                           " (n =", det.sum.total$n,")")   , las=1, cex.names=1, xlab="Total detections", horiz=T)
i <-1
for(i in 1:nrow(det.sum.total))
{
  tmp <- subset(dat, Species==det.sum.total$Species[i])
  det.sum.total$Locations[i] <- length(unique(tmp$Deployment.Location.ID))
}
par(mar=c(5,1,1,1))

barplot(det.sum.total$Locations/n.stat, las=1, cex.names=0.7, xlab="Proportion of sites detected", horiz=T, xlim=c(0,1))
abline(v=1, lty=2)

```

## Detection check
The following plot helps you determine if you have detections occuring outside of the times cameras are active. *Important note* You can still get detections outside of the activity period if you have decided that the field of view was shifted and the data is un-compariable to that which was collected earlier.  

```{r, include=F}
# Make species colour codes
tmp3 <- data.frame("Species"=unique(dat$Species),"Colour"= wheel("lightseagreen", num = length(unique(dat$Species))))

```


```{r detecion summary, echo=F, message=F, warning=F}

# Make a separate plot for each 20 stations For each 20 stations
# To do this make a plot dattaframe
tmp4 <- data.frame("Deployment.Location.ID"=plot.order, "Plot.grp"=ceiling(1:length(unique(eff$Deployment.Location.ID))/20))

eff <- left_join(eff,tmp4, by="Deployment.Location.ID")

j <- 1
for(j in 1:length(unique(eff$Plot.grp)))
{
    layout(matrix(c(1,1,1,2), 1, 4, byrow = TRUE))
    par(mar=c(2,6,1,1))
    
    plot(c(min(eff$Camera.Deployment.Begin.Date, na.rm=T), max(eff$Camera.Deployment.End.Date, na.rm=T)),      c(1,length(unique(eff$Deployment.Location.ID[eff$Plot.grp==j]))), las=1, ylab="", xlab="", type="n", yaxt="n")
    
    axis(2, at= 1:length(unique(eff$Deployment.Location.ID[eff$Plot.grp==j])), labels= unique(eff$Deployment.Location.ID[eff$Plot.grp==j]), las=1, cex.axis=1)
    #mtext("Camera Deployment ID", 2, 4)
    # Make lines for each of the cameras
    for(i in 1:length(unique(eff$Deployment.Location.ID[eff$Plot.grp==j])))
    {
      abline(h=i, col=rgb(0,0,0,0.1))
      tmp <- eff[eff$Deployment.Location.ID==unique(eff$Deployment.Location.ID[eff$Plot.grp==j])[i],]
      
      tmp2 <- dat[dat$Deployment.Location.ID==tmp$Deployment.Location.ID[1],]
      tmp2 <- left_join(tmp2, tmp3)
      points(tmp2$Date_Time.Captured, rep(i,nrow(tmp2)), pch="|", col= tmp2$Colour)
    
      for(k in 1:nrow(tmp))
        {
          lines(c(tmp$Camera.Deployment.Begin.Date[k],
                           tmp$Camera.Deployment.End.Date[k]),
                c(i,i), lwd=2)
        }
      }
    par(mar=c(0,0,1,0))
    plot.new()
    legend("topleft", legend=tmp3$Species, fill=tmp3$Colour, xpd=TRUE, cex=1.1 )

}

```

## Species metadata
Of the images classfied as containing animals, the proportion of photographs assigned to the following catagories are as follows:

### Sex
```{r sex, echo=F, include=F}
col.name <- "Sex"

tmp <- table(dat[,col.name][dat$Blank==FALSE], as.character(dat$Species[dat$Blank==FALSE]))
tmp <- as.data.frame.matrix(tmp)
dat[,col.name] <- factor(dat[,col.name])
cols <- wheel("lightseagreen", num = length(levels(dat[,col.name])))
# Name catagories with no data N\A for NOT ASSESSED
row.names(tmp)[row.names(tmp)==""] <- "N/A"
# make it the last level
tmp <- tmp[c(2:nrow(tmp),1),]
data_percentage <- apply(tmp, 2, function(x){x*100/sum(x,na.rm=T)})

```


```{r sex plot, echo=F, fig.height=sp.height}
layout(matrix(c(1,1,1,2), 1, 4, byrow = TRUE))
par(mar=c(5,10,1,1))
barplot(data_percentage , border="white",col= cols, ylab="", las=1, xlab="% of observations", cex.names=0.7, horiz=2)
par(mar=c(0,0,4,0))
plot.new()
legend("topleft", legend=row.names(tmp), fill=cols, xpd=TRUE, cex=1.1 )
```

### Age

```{r age, echo=F, include=F}
col.name <- "Age"

tmp <- table(dat[,col.name][dat$Blank==FALSE], as.character(dat$Species[dat$Blank==FALSE]))
tmp <- as.data.frame.matrix(tmp)
dat[,col.name] <- factor(dat[,col.name])
cols <- wheel("lightseagreen", num = length(levels(dat[,col.name])))
# Name catagories with no data N\A for NOT ASSESSED
row.names(tmp)[row.names(tmp)==""] <- "N/A"
# make it the last level
tmp <- tmp[c(2:nrow(tmp),1),]

data_percentage <- apply(tmp, 2, function(x){x*100/sum(x,na.rm=T)})

```


```{r age plot, echo=F, fig.height=sp.height}
layout(matrix(c(1,1,1,2), 1, 4, byrow = TRUE))
par(mar=c(5,10,1,1))
barplot(data_percentage , border="white",col= cols, ylab="", las=1, xlab="% of observations", cex.names=0.7, horiz=2)
par(mar=c(0,0,4,0))
plot.new()
legend("topleft", legend=row.names(tmp), fill=cols, xpd=TRUE, cex=1.1 )

```

### Behaviour

```{r Behaviour, echo=F, include=F}
col.name <- "Behaviour"

tmp <- table(dat[,col.name][dat$Blank==FALSE], as.character(dat$Species[dat$Blank==FALSE]))
tmp <- as.data.frame.matrix(tmp)

dat[,col.name]<- factor(dat[,col.name])
cols <- wheel("lightseagreen", num = length(levels(dat[,col.name])))
# Name catagories with no data N\A for NOT ASSESSED
row.names(tmp)[row.names(tmp)==""] <- "N/A"
# make it the last level
tmp <- tmp[c(2:nrow(tmp),1),]

data_percentage <- apply(tmp, 2, function(x){x*100/sum(x,na.rm=T)})

```


```{r behaviour plot, echo=F, fig.height=sp.height}
layout(matrix(c(1,1,1,2), 1, 4, byrow = TRUE))
par(mar=c(5,10,1,1))
barplot(data_percentage , border="white",col= cols, ylab="", las=1, xlab="% of observations", cex.names=0.7, horiz=2)
par(mar=c(0,0,4,0))
plot.new()
legend("topleft", legend=row.names(tmp), fill=cols, xpd=TRUE, cex=1.1 )

```



## Independent camera detections
```{r indepedents, echo=F, eval=T, message = F, warning = F}
# Remove onservations without animals detected
dat <- dat[dat$Blank==FALSE & is.na(dat$Species)==FALSE,]
dat$Species <- as.character(dat$Species)
dat$Deployment.Location.ID <- as.character(dat$Deployment.Location.ID)

# Order the datframe by Site, date
dat <- dat[order(dat$Deployment.Location.ID, dat$Date_Time.Captured),]


### NEW WAY
  dat <- dat %>%
  #filter(Species == i) %>%
  arrange(Project.ID,Deployment.Location.ID) %>%
  group_by(Deployment.Location.ID, Species) %>%
  mutate(duration = int_length(Date_Time.Captured %--% lag(Date_Time.Captured)))

# loop that assign group ID
dat$Event.ID <- 9999
  mins <- independent
  seq <- as.numeric(paste0(nrow(dat),0))
  seq <- round(seq,-(nchar(seq)))
for (i in 2:nrow(dat)) {
  dat$Event.ID[i-1]  <- paste0("E",format(seq, scientific = F))
  if(is.na(dat$duration[i]) | abs(dat$duration[i]) > (mins * 60)){
    seq <- seq + 1
  }
}

# Update the information for the last row
    # group ID  for the last row
 if(dat$duration[nrow(dat)] < (mins * 60)|
    is.na(dat$duration[nrow(dat)])){
   dat$Event.ID[nrow(dat)] <- dat$Event.ID[nrow(dat)-1]
 } else{
   dat$Event.ID[nrow(dat)] <- paste0("E",format(seq+1, scientific = F))
 }

# If there is no minimum groupsize take number of animals
if(!"Minimum.Group.Size" %in% colnames(dat)) {dat$Minimum.Group.Size <- dat$Number.of.Animals}

# Calculate the event length and size

  # find out the last and the first of the time in the group
  top <- dat %>% group_by(Event.ID) %>% top_n(1,Date_Time.Captured) %>% select(Event.ID, Date_Time.Captured)
  bot <- dat %>% group_by(Event.ID) %>% top_n(-1,Date_Time.Captured) %>% select(Event.ID, Date_Time.Captured)
  names(bot)[2] <- c("Date_Time.Captured_end")
  dec_no <- dat %>% group_by(Event.ID) %>% summarise(n())
  event_grp <- dat %>% group_by(Event.ID) %>% summarise(max(Minimum.Group.Size))

  # caculate the duration
  diff <-  top %>% left_join(bot, by="Event.ID") %>%
      mutate(duration=abs(int_length(Date_Time.Captured %--% Date_Time.Captured_end))) %>%
      left_join(event_grp, by="Event.ID")%>%
      left_join(dec_no, by="Event.ID")

  # Remove duplicates
  diff <- diff[duplicated(diff)==FALSE,]

  names(diff) <- c("Event.ID","Date_Time.end","Date_Time.start","Event.Duration","Event.Groupsize","Event.Observations")
  diff$Date_Time.end<-NULL;diff$Date_Time.start<-NULL
  dat$duration <-NULL
  # Merge the data
  dat <-  dat %>%
   left_join(diff,by="Event.ID")

# Subset to the first observation in each event

  # Subset to 30 minute indepedenents
ind.dat <- dat[!duplicated(dat$Event.ID),]
ind.dat <- as.data.frame(ind.dat)
ind.dat$Species <-as.factor(ind.dat$Species)

# Save it for a rainy day
write.csv(ind.dat, paste0("Output data/",dat$Project.ID[1], "_",independent ,"min_Independent.csv"), row.names = F)

```

Using an independance threshold of `r independent` minutes, the number of detections is reduced to `r nrow(ind.dat)`. The rest of the analyses are conducted with this data. The summary of detections is as follows:

```{r ind captures, echo=F, fig.height=sp.height, eval=T}

layout(matrix(c(1,1,2), 1, 3, byrow = TRUE))
det.sum.total <- as.data.frame(count(ind.dat[ind.dat$Blank==FALSE,], Species))
det.sum.total <- det.sum.total[order(det.sum.total$n),]

par(mar=c(5,16,1,1))
barplot(det.sum.total$n, names.arg = paste0(det.sum.total$Species,
                                           " (n =", det.sum.total$n,")"), las=1, cex.names=1, xlab="Total detections", horiz=T)
i <-1
for(i in 1:nrow(det.sum.total))
{
  tmp <- subset(ind.dat, Species==det.sum.total$Species[i])
  det.sum.total$Locations[i] <- length(unique(tmp$Deployment.Location.ID))
}
par(mar=c(5,1,1,1))

barplot(det.sum.total$Locations/n.stat, las=1, cex.names=0.7, xlab="Proportion of sites detected", horiz=T, xlim=c(0,1))
abline(v=1, lty=2)

```

## Group size distribution

```{r group size, echo=F, eval=T,fig.height=sp.height}
par(mfrow=c(1,1))
par(mar=c(5,10,1,1))
plot(jitter(as.numeric(ind.dat$Species))~jitter(ind.dat$Minimum.Group.Size), xlab="Minimum group size", yaxt="n", las=1, ylab="")
axis(2, 1:length(unique(ind.dat$Species)), labels=levels(ind.dat$Species), las=2, cex.axis=0.6)

```


# Site-level species covariance
This plot shows the covariance between different species at the site level for species with >5 unique detections. For example, if you typically get lots of caribou and bears at the same site, they will have positive covariance. If you get caribou where you dont get bears, they will have negative covariance.

```{r covariance, echo=F, fig.height=sp.height,fig.width=sp.height, eval=T}
par(mfrow=c(1,1))
tmp <- as.data.frame.matrix(table(ind.dat$Deployment.Location.ID, ind.dat$Species))
tmp <- tmp[colSums(tmp)>5]
M <- cor(tmp)

corrplot(M, method="color", #col=matrix(col(200)),
         type="upper", order="hclust",
         #addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=45, #Text label color and rotation
         # Combine with significance
         #p.mat = p.mat, sig.level = 0.01, insig = "blank",
         # hide correlation coefficient on the principal diagonal
         diag=FALSE
         )

```


# Calculate relative abundance
Note, when calculating relative abundance, we use the minimum group size column. 
```{r relative abundance calc, echo=F, warning=F, message=F, eval=T}

det.sum.site <- as.data.frame(table(ind.dat$Deployment.Location.ID, ind.dat$Species))
colnames(det.sum.site) <- c("Deployment.Location.ID","Species", "Detections")
det.sum.site$Individuals <- NA

i <- 1
for(i in 1:nrow(det.sum.site))
{
   tmp <- subset(ind.dat, Deployment.Location.ID==as.character(det.sum.site$Deployment.Location.ID)[i] &
              Species==as.character(det.sum.site$Species)[i])
   det.sum.site$Individuals[i] <- sum(tmp$Minimum.Group.Size, na.rm=T)
}

# Join with the station effort
CR.site <- left_join(det.sum.site,aggregate(Days~Deployment.Location.ID, data=eff,  FUN=sum, na.rm=T) )
CR.site$CR.100 <- round((CR.site$Individuals/CR.site$Days)*100,3)
# Add station locations
CR.site <- left_join(CR.site, sta[, c("Deployment.Location.ID", "Latitude", "Longitude")])

```


## Site-level temporal plots

### Summary
Across all sites and species:

```{r, echo=F, eval=T}
# Capture rates through time
focal.sp <- as.character(det.sum.total[det.sum.total$n>0,]$Species)
focal.sp <- focal.sp[order(focal.sp)]
# Remove any blanks
focal.sp <- focal.sp[focal.sp!=""]

# We need to know how many detections there are in each month -> create a row lookup
# This is just a list of ever day a camera was active.

tmp <- eff[is.na(eff$Camera.Deployment.End.Date)==F,]
daily.lookup <- list()
for(i in 1:nrow(tmp))
{
  if(as.Date(tmp$Camera.Deployment.Begin.Date[i])!=as.Date(tmp$Camera.Deployment.End.Date[i]))
  {
    daily.lookup[[i]] <- data.frame("Date"=seq(as.Date(tmp$Camera.Deployment.Begin.Date[i])+1, as.Date(tmp$Camera.Deployment.End.Date[i]), by="days"), "Deployment.Location.ID"=tmp$Deployment.Location.ID[i])
  }
}
row.lookup <- do.call(rbind, daily.lookup)

# Now determine capture rates
# Make a data frame by month and year
mon.dat <- unique(substr(ind.dat$Date_Time.Captured, 1,7))
mon.dat <- data.frame("Month"=mon.dat[order(mon.dat)], "Effort"= NA)
mon.dat[as.character(focal.sp)] <- NA
i<-1
for(i in 1:nrow(mon.dat))
{
  mon.dat$Effort[i] <- nrow(subset(row.lookup, substr(row.lookup$Date,1,7)==mon.dat$Month[i]))
  mon.dat$Total.CR[i] <- (nrow(subset(ind.dat, substr(ind.dat$Date_Time.Captured,1,7)==mon.dat$Month[i]))/mon.dat$Effort[i])*100
}

for(i in 1:length(focal.sp))
{
  for(j in 1:nrow(mon.dat))
  {
    tmp <- subset(ind.dat, Species==as.character(focal.sp)[i] & substr(ind.dat$Date_Time.Captured,1,7)==mon.dat$Month[j])
    mon.dat[j, as.character(focal.sp[i])] <- (nrow(tmp)/mon.dat$Effort[j])*100
  }
}

mon.dat$timestamp <- strptime(paste0(as.character(mon.dat$Month),"-15"), "%Y-%m-%d")

# Remove any silly values 
mon.dat <- mon.dat[is.infinite(mon.dat$Total.CR)==F,]

```


```{r overall CR, echo=F, fig.height=4, eval=T}

par(mfrow=c(1,2))

plot(mon.dat$timestamp, mon.dat$Effort, ylab="Monthly Effort (days)", xlab="Date", type="l", las=1)
points(mon.dat$timestamp, mon.dat$Effort, pch=19, col=rgb(0,0,0,0.4))

# Overall capture rate
plot(mon.dat$timestamp, mon.dat$Total.CR, ylab="Monthly total CR per 100 days", xlab="Date", type="l", las=1, ylim=c(0, max(mon.dat$Total.CR)))
points(mon.dat$timestamp, mon.dat$Total.CR, pch=19, col=rgb(0,0,0,0.4))

```

### Species-specific temporal trends
Species level variation in monthly capture rates are as follows:

```{r, echo=F, eval=T}
par(mfrow=c(2,3))
for(i in 1:length(focal.sp))
{
  plot(mon.dat$timestamp, mon.dat[,as.character(focal.sp)[i]], ylab="Capture Rate per 100 days", xlab="", type="l", las=1, main=focal.sp[i])
  points(mon.dat$timestamp, mon.dat[,as.character(focal.sp)[i]], pch=19, col=rgb(0,0,0,0.4))
}

```


## Spatial plots
Kriged spatial plots of the capture rate per 100 days, scaled within each species accross the study area. These plots are to simply a give an idea of where you are catching each species. Only for species with > 20 captures.

```{r, echo=F, fig.height=8, eval=spatial.plots}

focal.sp <- as.character(det.sum.total[det.sum.total$n>20,]$Species)
focal.sp <- focal.sp[order(focal.sp)]
# Remove any blanks
focal.sp <- focal.sp[focal.sp!=""]



par(mfrow=c(2,2))
for(i in 1:length(focal.sp))
{
  p <- data.frame(x=CR.site$Longitude[CR.site$Species==focal.sp[i]], y=CR.site$Latitude[CR.site$Species==focal.sp[i]])#
  p <- p[chull(p),]
  p <- list(p)

  # Krig your raster
   x <- CR.site$Longitude[CR.site$Species==focal.sp[i]]
  y <- CR.site$Latitude[CR.site$Species==focal.sp[i]]
  z <- CR.site$CR.100[CR.site$Species==focal.sp[i]]# Krige and create the map
  kriged <- kriging(x, y, z, polygons=p, pixels=300, lags=5)
  image(kriged, xlim = extendrange(x), ylim = extendrange(y),
       col=hcl.colors(20, "Oranges", rev = TRUE), breaks=c(seq(0,max(z),length.out = 21) ), asp=1, las=1, main=focal.sp[i])
  #legend(-110.9,57.75,c(seq(0,max(z),length.out = 21) ),col=hcl.colors(20, "Oranges", rev = TRUE) )
  points(x,y, pch=19, cex=0.8, col=rgb(0,0,0,0.5))
}

```




